### 2014-05-14 ms_probaweb.tex

\textbf{Title:} A quantitative framework for network biogeography\\
% Alternative: The distribution of ecological interactions 
% Alternative: The biogeography of ecological interactions
% Alternative: Community (macro)ecology: integrating species interactions and species distributions

@@

3: \\

@@

Ecology textbooks define the structure of an ecological community as
\emph{the pool of species occupying a given location at a given time, and
the way these species interact} (ref to Morin?). It is therefore surprising
that ecological research on the variation of community structure has focused
on species turnover (refs), almost entirely neglecting variation in the way
species interact (refs).

@@

@@

\newpage
%========================================================%
\section*{Interpretation: the integrated niche}

% TO BE COMPLETED

>>>>

\textbf{Title:} Scaling up patterns of emerging niche complexity in the metaweb of life -- an overarching conceptual synthesis and quantitative framework\\
% Alternative: The distribution of ecological interactions 
% Alternative: The biogeography of ecological interactions
% Alternative: Community (macro)ecology: integrating species interactions and species distributions

@@

3: University of Canterbury at Christchurch, School of Biological Sciences,\\

@@

Ecology textbooks define the structure of an ecological community as \emph{the
pool of species occupying a given location at a given time, and the way
these species interact} (ref to Morin?). It is therefore surprising that
ecological research on the variation of community structure has focused
on species turnover (refs), almost entirely neglecting variation in the
way species interact (refs). This poses two challenges for the cohesion
of community ecology as a unified field. First, we need to account, in
an explicit way, for species interactions in our understanding of species
occurrence and distributions (refs). Second, we need to expand the work that
has been done in "species-based" community ecology, \emph{i.e.} measuring
and predicting variation in species assemblages, into our study of species
interactions. Here we argue that both of these challenges can be adressed
as the same time, by considering that species interactions are not a fixed
covariate in species distribution models, but react in complex ways to the
presence and absence of species. Adopting this point of view provides a
more unified way of community ecology, as a field seeking to undertand the
distribution of species and their interactions.

@@

%%% FORMER NICHE SECTION

%%% END OF FORMER NICHE SECTION

@@
